% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass{cover} 
\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\newsectionwidth{0pt}  % So the text is not indented under section headings
\usepackage{fancyhdr}  % use this package to get a 2 line header
\renewcommand{\headrulewidth}{0pt} % suppress line drawn by default by fancyhdr
\setlength{\headheight}{12pt} % allow room for 2-line header
\setlength{\headsep}{12pt}  % space between header and text
\setlength{\headheight}{12pt} % allow room for 2-line header
\pagestyle{fancy}     % set pagestyle for document
\rhead{ {\it Manasa Mahesh}\\{\it p. \thepage} } % put text in header (right side)
\cfoot{}                                     % the foot is empty
\topmargin=-0.8in % start text higher on the page
\usepackage{geometry} % to change the page dimensions
\geometry{a4paper} % or letterpaper (US) or a5paper or....
\geometry{margin=1.0in} % for example, change the margins to 2 inches all round
\addtolength{\topmargin}{-5mm}

\begin{center}
\huge\bf Manasa Mahesh \\ % Your name
%\vspace{20pt} \hrule height 1pt % If you would like a horizontal line separating the name from the address, uncomment the line to the left of this text
20 Skytop Garden Apt 10 Parlin NJ 08859 \\ (732) 210-8297 % Your address and phone number
\end{center} 
\vfill

\signature{Manasa Mahesh} % Your name for the signature at the bottom
\begin{document}
\thispagestyle{empty} % this page has no header  


Dear Hiring Manager,
\vspace{0.2in}
\\* 
I am a graduate student at the University of California, Irvine (graduated in
December 2013) with specialization in Computer Engineering. I am actively
looking
for full time opportunities as a Software Developer - preferably in the field
of
embedded systems/compilers. \vspace{0.2in}\\*
Four years of relevant work experience, added with my relevant research work in
UCI and successful completion of advanced systems related courses makes me
believe that I am a strong candidate for this position. \vspace{0.2in}\\*
My work with Alcatel Lucent (India) mainly involved low level API development. 
Here, I worked primarily on Linux based embedded systems developing features
which require working knowledge of {\bfseries device drivers, file systems,
boot process},
Shell scripting, inter-process communication, and TCP/IP stack. \vspace{0.2in}\\*
To add to this knowledge, I have also completed advanced courses like high
performance computing, computer architecture, program analysis, memory models and compilers,
system on chip software synthesis, advanced compiler construction and a study
on Heterogenous architecture({\bfseries ARM Big.Little}). \vspace{0.2in}\\*
I have worked on a research project on LLVM open source compiler
under Prof. Michael Franz. This project aims to harness compiler-generated
software diversity for defense purposes using a multi-compiler diversification
engine. I worked towards automatically generating unique yet functionally
identical
binaries/mobile apps for each download request for a {\bfseries ARM processor} (Panda board). \vspace{0.2in}\\*
As a part of my acedemia, I have worked on emulating an {\bfseries ARMv8 ISA} using
{\bfseries Foundation Models} and booting up a Linux kernel on top of that. As part of
this project, I had to interact with Linaro for support with kernel image, rootfs and
the cross-compiler. \vspace{0.2in}\\*
During the summer of 2013, I interned at Broadcom (Irvine). Here, I developed a
tool using the open source compiler infrastructure “LLVM/Clang” to perform
static code analysis. \vspace{0.2in}\\*
I look forward for an opportunity to demonstrate my abilities and would be
eager to
hear from you in the near future. Thank you for your time and consideration.\\*
Eagerly looking forward to your reply,\\ \\\\
Pavan Pattanada\\
pattanad@uci.edu\\
(949)-743-4307\\
www.linkedin.com/in/pavanpattanada\\
 
\end{document}













