% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass{system} 
\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\newsectionwidth{0pt}  % So the text is not indented under section headings
\usepackage{fancyhdr}  % use this package to get a 2 line header
\renewcommand{\headrulewidth}{0pt} % suppress line drawn by default by fancyhdr
\setlength{\headheight}{12pt} % allow room for 2-line header
\setlength{\headsep}{12pt}  % space between header and text
\setlength{\headheight}{12pt} % allow room for 2-line header
\pagestyle{fancy}     % set pagestyle for document
\rhead{ {\it Manasa Mahesh}\\{\it p. \thepage} } % put text in header (right side)
\cfoot{}                                     % the foot is empty
\topmargin=-0.8in % start text higher on the page
\usepackage{geometry} % to change the page dimensions
\geometry{a4paper} % or letterpaper (US) or a5paper or....
\geometry{margin=0.3in} % for example, change the margins to 2 inches all round
\addtolength{\topmargin}{-5mm}
%\fontencoding{T1}
%\fontfamily{garamond}
%\fontseries{m}
%\fontshape{it}
%\fontsize{14}{15}
%\selectfont

\begin{document}
\thispagestyle{empty} % this page has no header  
\address{{\huge Manasa Mahesh}\vspace{12pt} \\C++ Developer actively seeking
for new opportunities}
%\name{MANASA MAHESH\\[12pt]}% the \\[12pt] adds a blank line after name

\address{20 Skytop Gardens, Apt 10, Parlin, NJ 08859}      
                                      
\address{\hfill 20 Skytop Gardens, Apt 10, Parlin, NJ 08859\\ \hfill {http://www.linkedin.com/in/manasamahesh}\\
  \hfill manasa.mahesh7@gmail.com \\ \hfill (732)-333-5777 }



\begin{resume}
\section {TECHNICAL SKILLS}
\hrulefill
   \begin{itemize} \itemsep -2pt % reduce space between items
   \item Languages: C, C++, XML, DBMS, Shell script
   \item IDE/Tools: Eclipse, Source Insight, FTP, SCME, Eclipse, Function Point
   \item Platforms: Windows, Unix
 \end{itemize}
%\vspace{0.2in} 
\vspace{5pt}
 
\section{EDUCATION} 
\hrulefill\\
{\bfseries Bachelor of Engineering, Computer Science} \\ % \sl will be bold italic in
					 % New Century Schoolbook (or
					 % any postscript font) and
					 % just slanted in Computer
					 % Modern (default) font 
Sri Jayachamarajendra College of Engineering, Mysore, India
\hspace{0.2in}  {\bfseries GPA 3.6} (equivalent)
\hfill    {\bfseries June 2010}
  
%\vspace{0.2in} 
\vspace{5pt}
\section{{PROFESSIONAL EXPERIENCE}} 
\hrulefill \\
{\bfseries IBM} \hfill         {\bfseries Jul 2010 - Present} \\
{\bfseries NC3 Application team}       \hfill   {\bfseries (Associate Software
Engineer)}\\
 NC3 is a web based tool for Designing, Configuration, Maintainance and Network
 Management of a repository containing Customer Premise Equipment (CPE) and
 related Site and Connectivity/VPN data. 
   \begin{itemize} \itemsep 2pt % reduce space between items
   \item Worked as part of the design and development of projects which helped
   me to widen the knowledge on Object Oriented Programming principles
   \item Worked on multiple enhancements for this project and fixed issues
   which were multi-threaded in nature.
   \item  Mentored and trained new recruits; developed a program to streamline new
 recruit on-boarding process and created training materials to improve 
 productivity by 10\%
   reported issues
   \item {\bfseries PROJECTS}
    \begin{itemize} \itemsep 2pt

        \item {\bfseries Core Dump Analyser} \hfill {\bfseries [C++, Shell Scripting]}\\
        Core Dump analysis is quite complex and time consuming as it involves in-depth knowledge and expertise on various domains 
        like processor architecture and operating systems. To ease the analysis part,
        an intuitive, intelligent and easy to use {\bfseries web based static analyzer}
        was developed using {\bfseries C++ and STL's} 
        It also does various known checks on the dump to help an Engineer perform RCA
        of an issue faster. 
        \hspace{0.1in}

        \item {\bfseries Extracts} \hfill { \bfseries [SQL, C++,
        Multi-threading]}\\
        Nc3 application is an inventory to store customer’s data. Customers came up 
        with the new requirement where they wanted their data to be sent in bulk. Till
        then, customer data was sent based on the order received. A new
        architecture was developed containing scripts and batch programs to fetch the data on
        daily basis focusing on {\bfseries Performance Tuning} by optimizing
        {\bfseries SQL} queries. This architecture
        design was successfully implemented and presented to whole AT\&T account 
        \hspace{0.1in} 

        \item {\bfseries Automation project } \hfill {\bfseries [C++, OOPS, Batch
        Programming]} \\
        As a part of this project, manual work being done by network engineers was automated.
        This project takes a couple of minutes to complete all the processing (typically taken hours if done manually).  
        \begin{itemize} \itemsep 2pt 
            \item Improved the efficiency of the product by automating the user creation
            process.
            \item Used C++ STLs, Design Patterns, Data Strutures, XML Parsers and Batch
            Programming.
            \item  Developed reverse engineering document,  Design document
            for the new architecture, Collated the concepts developed and used by several 
            engineers, to increase the productivity of the engineering team.
            \item  Took initiative in preparing estimates and counting Function points for the
            projects.
        \end{itemize}
    \end{itemize}

 \end{itemize}

\vspace{5pt}
\section {ACCOMPLISHMENTS AND HIGHLIGHTS}
\hrulefill
\begin{itemize} \itemsep 2pt
\item Received multiple {\bfseries team level, account level e-awards} for my performance
and technical excellence.
\item Rated among top {\bfseries 10\%} throughout my tenure in IBM.
\item Awarded {\bfseries “Service Excellence Award”} for the dedication and excellence in
project delivery.
\item Awarded {\bfseries “Eminence and Excellence Award”} for acting as SPOC for project
delivery.
\item Awarded {\bfseries “HALL OF FAME”} for the innovative core dump analyzer tool developed
\item Awarded {\bfseries “BEST OF IBM”} for mentoring the graduate hires.
\end{itemize}
 
 
\end{resume} 
\end{document}













